Methods for Large Scale Learning to Rank

### 2014-02-24 report/BenchmarkResults.tex
feature tabel met formules af :)

\chapter{LETOR}
The LETOR benchmark set was first released by Microsoft Research Asia in April 2007 to solve the absence of a experimental platform for Learning-to-Rank at that time. LETOR has been updated several times since: LETOR 2.0 was released at the end of 2007, LETOR 3.0 in December 2008 and LETOR 4.0. The original benchmark\cite{Liu2007b} as released in 2007 contained
\section{Benchmark characteristics}
\begin{table}[!h]
\scalebox{0.87}{
\begin{tabular}{p{0.29cm}|p{7.26cm}||p{0.29cm}|p{9.55cm}}
 \textbf{ID} & \textbf{Feature Description} & \textbf{ID} & \textbf{Feature Description}\\ 
 \hline
1 & \ac{TF} of body					& 36& LMIR.JM of body\\
2 &	\ac{TF} of anchor				& 37& LMIR.JM of anchor\\
3 & \ac{TF} of title				& 38& LMIR.JM of title\\
4 & \ac{TF} of \ac{URL}				& 39& LMIR.JM of \ac{URL}\\
5 & \ac{TF} of whole document		& 40& LMIR.JM of whole document\\

@@

31& LMIR.DIR of body\\
32& LMIR.DIR of anchor\\
33& LMIR.DIR of title\\
34& LMIR.DIR of \ac{URL}\\
35& LMIR.DIR of whole document\\
\end{tabular}
}
\caption{Features of the LETOR .GOV dataset, obtained from Qin et al\cite{Qin2010}}
\label{tbl:features_gov}
\end{table}
\section{Results}

>>>>

\chapter{LETOR}
The LETOR benchmark set was first released by Microsoft Research Asia in April 2007 to solve the absence of a experimental platform for Learning-to-Rank at that time. LETOR has been updated several times since: LETOR 2.0 was released at the end of 2007, LETOR 3.0 in December 2008 and LETOR 4.0 in July 2009. The original LETOR benchmark collection\cite{Liu2007b} as released in 2007 contained two data sets: the OHSUMED collection and the .gov collection. The OHSUMED collection is a subset of the medical publication database MEDLINE and contains medical publications from 270 journals that were published between 1987 and 1991. The .gov collection is a web crawl obtained in January 2002, which was used for the TREC web track in 2003 and 2004.\\
\section{Benchmark characteristics}
\begin{table}[!h]
\scalebox{0.87}{
\begin{tabular}{p{0.29cm}|p{7.26cm}||p{0.29cm}|p{9.55cm}}
 \textbf{ID} & \textbf{Feature Description} & \textbf{ID} & \textbf{Feature Description}\\ 
 \hline
1 & \ac{TF} of body					& 36& LMIR.JM of body\\
2 &	\ac{TF} of anchor				& 37& LMIR.JM of anchor\\
3 & \ac{TF} of title				& 38& LMIR.JM of title\\
4 & \ac{TF} of \ac{URL}				& 39& LMIR.JM of \ac{URL}\\
5 & \ac{TF} of whole document		& 40& LMIR.JM of whole document\\

@@

31& LMIR.DIR of body\\
32& LMIR.DIR of anchor\\
33& LMIR.DIR of title\\
34& LMIR.DIR of \ac{URL}\\
35& LMIR.DIR of whole document\\
\end{tabular}
}
\caption{Features of the LETOR .GOV dataset, obtained from Qin et al\cite{Qin2010}}
\label{tbl:features_gov}
\end{table}

\begin{table}[!h]
\scalebox{0.87}{
\begin{tabular}{p{0.29cm}|p{6.88cm}||p{0.29cm}|p{6.90cm}}
 \textbf{ID} & \textbf{Feature Description} & \textbf{ID} & \textbf{Feature Description}\\ 
 \hline
1 & $\sum\nolimits_{q_i \in q \cap d}c(q_i, d)$ of title					& 24&  $\sum\nolimits_{q_i \in q \cap d}c(q_i,d)\cdot log(\frac{|C|}{df(q_i)})$ of abstract\\
2 &	$\sum\nolimits_{q_i \in q \cap d}log(c(q_i, d)+1)$ of title				& 25& $\sum\nolimits_{q_i \in q \cap d} log(\frac{c(q_i,d)}{|d|}) \cdot \frac{|C|}{c(q_i,C)}+1$ of abstract\\
3 & $\sum\nolimits_{q_i \in q \cap d}\frac{c(q_i,d)}{|d|}$ of title				& 26& BM25 of abstract\\
4 & $\sum\nolimits_{q_i \in q \cap d}log(\frac{c(q_i,d)}{|d|}+1)$ of title				& 27& $log($BM25$)$ of abstract\\
5 & $\sum\nolimits_{q_i \in q \cap d}log(\frac{|C|}{df(q_i)})$ of title		& 28& LMIR.DIR of abstract\\

6 & $\sum\nolimits_{q_i \in q \cap d}log(log(\frac{|C|}{df(q_i)}))$ of title 				& 29& LMIR.JM of abstract\\
7 & $\sum\nolimits_{q_i \in q \cap d}log(\frac{|C|}{c(q_i,C)}+1)$ of title 				& 30& LMIR.ABS of abstract\\
8 & $\sum\nolimits_{q_i \in q \cap d}log(\frac{c(q_i,d)}{|d|} \cdot \frac{|C|}{df(q_i)}+1)$ of title 				& 31& $\sum\nolimits_{q_i \in q \cap d}c(q_i, d)$ of title + abstract\\
9 & $\sum\nolimits_{q_i \in q \cap d}c(q_i,d)\cdot log(\frac{|C|}{df(q_i)})$ of title 			& 32&	$\sum\nolimits_{q_i \in q \cap d}log(c(q_i, d)+1)$ of title + abstract\\
10& $\sum\nolimits_{q_i \in q \cap d} log(\frac{c(q_i,d)}{|d|}) \cdot \frac{|C|}{c(q_i,C)}+1$ of title		& 33& $\sum\nolimits_{q_i \in q \cap d}\frac{c(q_i,d)}{|d|}$ of title + abstract\\

11& BM25 of title 			& 34& $\sum\nolimits_{q_i \in q \cap d}log(\frac{c(q_i,d)}{|d|}+1)$ of title + abstract\\
12& $log($BM25$)$ of title 			& 35& $\sum\nolimits_{q_i \in q \cap d}log(\frac{|C|}{df(q_i)})$ of title + abstract\\
13& LMIR.DIR of title 			& 36& $\sum\nolimits_{q_i \in q \cap d}log(log(\frac{|C|}{df(q_i)}))$ of title + abstract\\
14& LMIR.JM of title			& 37& $\sum\nolimits_{q_i \in q \cap d}log(\frac{|C|}{c(q_i,C)}+1)$ of title + abstract\\
15& LMIR.ABS of title	& 38& $\sum\nolimits_{q_i \in q \cap d}log(\frac{c(q_i,d)}{|d|} \cdot \frac{|C|}{df(q_i)}+1)$ of title + abstract\\

16& $\sum\nolimits_{q_i \in q \cap d}c(q_i, d)$ of abstract		& 39& $\sum\nolimits_{q_i \in q \cap d}c(q_i,d)\cdot log(\frac{|C|}{df(q_i)})$ of title + abstract\\
17& $\sum\nolimits_{q_i \in q \cap d}log(c(q_i, d)+1)$ of abstract		& 40& $\sum\nolimits_{q_i \in q \cap d} log(\frac{c(q_i,d)}{|d|}) \cdot \frac{|C|}{c(q_i,C)}+1$ of title + abstract\\
18& $\sum\nolimits_{q_i \in q \cap d}\frac{c(q_i,d)}{|d|}$ of abstract		& 41& BM25 of title + abstract\\
19& $\sum\nolimits_{q_i \in q \cap d}log(\frac{c(q_i,d)}{|d|}+1)$ of abstract		& 42& $log($BM25$)$ of title + abstract\\
20& $\sum\nolimits_{q_i \in q \cap d}log(\frac{|C|}{df(q_i)})$ of abstract	& 43& LMIR.DIR of title + abstract\\

21& $\sum\nolimits_{q_i \in q \cap d}log(log(\frac{|C|}{df(q_i)}))$ of abstract					& 44& LMIR.JM of title + abstract\\
22&  $\sum\nolimits_{q_i \in q \cap d}log(\frac{|C|}{c(q_i,C)}+1)$ of abstract					& 45& LMIR.ABS of title + abstract\\
23& $\sum\nolimits_{q_i \in q \cap d}log(\frac{c(q_i,d)}{|d|} \cdot \frac{|C|}{df(q_i)}+1)$ of abstract					& & \\
\end{tabular}
}
\caption{Features of the LETOR OHSUMED dataset, obtained from Qin et al\cite{Qin2010}}
\label{tbl:features_gov}
\end{table}
\section{Results}
